### 2017-10-10 manuscript.rmd
updated to new species tree

	# Biological
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

@@

	# Set paths to input data
	json_name = "agalma/agalma.json"

@@

  # Load and parse phylogenies and expression data from the
  # json file produced by agalma

	# Eventually species tree will be parsed from json, for now specify temporary tree
	# agalma.data = jsonlite::fromJSON( json_name )
	# species_tree = read.tree( text=agalma.data$speciestree )

	# For now, specify the tree as plain text
	species_tree_text = "(((((((((((((((Nanomia_bijuga:0.120563,Agalma_elegans:0.0575132)100:0.0339417,Lychnagalma_utricularia:0.0749548)100:0.0140092,(Cordagalma_sp_:0.117222,Forskalia_asymmetrica:0.0739343)100:0.0113754)100:0.0159061,(Resomia_ornicephala:0.036642,Frillagalma_vityazi:0.0604811)100:0.0190101)100:0.024866,(((Physonect_sp_:0.0317839,Marrus_claudanielis:0.0284231)100:0.0125343,Stephalia_dilata:0.0841317)82:0.00517707,Erenna_richardi:0.0414121)100:0.0124079)100:0.0161254,((((Chelophyes_appendiculata:0.0574339,Abylopsis_tetragona:0.0562432)100:0.11489,(Chuniphyes_multidentata:0.0345263,Kephyes_ovata:0.0306657)100:0.0273795)100:0.0225022,Lilyopsis_fluoracantha:0.197884)100:0.018739,((Prayidae_D27SS7:0.0600685,Prayidae_D27D2:0.0464896)100:0.00909199,Hippopodius_hippopus:0.100508)100:0.011385)100:0.0822577)100:0.0232853,((Bargmannia_elongata:0.0175209,Bargmannia_amoena:0.0201366)100:0.0187736,Bargmannia_lata:0.031329)100:0.0887499)100:0.0300558,((Apolemia_sp_:0.0291459,Apolemia_lanosa:0.0332208)95:0.00837843,Apolemia_white:0.0422333)100:0.0841266)100:0.0313749,(Physalia_physalis:0.082276,Rhizophysa_filiformis:0.105414)100:0.0750894)100:0.133951,(Hydractinia_symbiolongicarpus:0.100907,Podocoryna_carnea:0.246708)100:0.104625)99:0.0219002,Clytia_hemisphaerica:0.331138)97:0.0219604,(Hydra_magnipapillata:0.268083,Ectopleura_larynx:0.273479)100:0.11387)100:0.0827444,Aegina_citrea:0.408585)100:0.148851,(Atolla_vanhoeffeni:0.282409,Alatina_alata:0.328817):0.058436)100:0.419544,(Aiptasia_pallida:0.199088,Nematostella_vectensis:0.188379)100:0);"

	species_tree = read.tree( text=species_tree_text )

@@

@@

	# species_tree = ape::root( species_tree, c( "Nematostella_vectensis", "Aiptasia_pallida" ), resolve.root=TRUE )
	# species_tree = ape::unroot(species_tree)

>>>>

	# Biological
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

@@

	# Set paths to input data
	input_file_ml = "agalma/Outfiles/RAxML_bipartitions.alignment.fa"

@@

	species_tree = ape::read.tree( input_file_ml )

@@

	species_tree = 
	  ape::root( 
	    species_tree, 
	    c( "Nematostella_vectensis", "Aiptasia_pallida" ), 
	    resolve.root=TRUE 
	   )

  #medusozoa_node = getMRCA( species_tree, c("Alatina_alata", "Nanomia_bijuga") )

  #species_tree = phytools::reroot( species_tree, medusozoa_node )

@@

	# species_tree = ape::unroot(species_tree)
